### 2018-09-28 ms.tex
Add n for all analyses.

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
For Senegal we selected 2015 for both prevalence data (n = ) and surveillance data (n =).
Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.

>>>>

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
For Indonesia we selected 2012 for surveillance data ($n = 380$) and 2010 for  prevalence data ($n = 969$).
For Senegal we selected 2015 for both surveillance data ($n = 46$) and prevalence data ($n = 216$). % update todo
Finally, for Madagascar we selected 2013 for both surveillance ($n = 110$) and prevalence ($n = 290$) data.
